Order statistics and numerical optimization

### 2019-12-25 inst/order.Rmd
more tweaks on randomizer branch

```{r}
f <- function(p,n){c(p,rep((1-p)/n,n-1))}
sss <- f(0.9999,9)  # sensible start point, close (?) to the evaluate
evaluate2 <- maxp(H,startp=sss)
maxlike2 <- loglik(indep(evaluate2),H)
```

@@

```{r}
evaluate3 <- maxp(H,vsssp(4,10))
maxlike3 <- loglik(indep(evaluate3),H)
dotchart(evaluate3,pch=16)
```

>>>>

```{r}
f <- function(p,n){c(p,rep((1-p)/n,n-1))}
sss <- f(0.99,9)  # sensible start point, close (?) to the evaluate
evaluate2 <- maxp(H,startp=sss)
maxlike2 <- loglik(indep(evaluate2),H)
```

@@

```{r}
evaluate3 <- maxp(H,vsssp(2,10))
maxlike3 <- loglik(indep(evaluate3),H)
dotchart(evaluate3,pch=16)
```
